## Getting the Story Straight

Firms face incentives to evade sales taxes by overreporting their input costs. Firms overreport their cost by acquiring fake invoices to claim additional deductions of their sales taxes, maximizing after-tax profits. The higher the sales tax, the greater the incentive to evade. However, the probability of detection and the threat of penalties limit how much firms overreport.

The key incentive for firms is the **effective sales tax rate** — the amount firms ultimately pay or receive from the tax authority. The effective tax rate is calculated as the difference between the total sales tax charged by the firm on its sales and the total sales tax paid by the firm on its inputs, divided by total sales. A positive difference indicates what the firm should pay to the government. If the difference is negative, the firm receives a refund from the tax authority.

$$
\begin{aligned}
\tau &= \frac{\tau_0P_tY_{it} - \tau_1\rho_t M_{it}}{P_tY_{it}} \\
&= \tau_0 - \tau_1 \beta
\end{aligned}
$$

In Colombia, the total amount charged by the firm as sales tax depends on the statutory tax rate of each product sold domestically; **exports are exempt** from sales tax. Low statutory sales tax rates and exempt products result in lower sales tax collected by the firm and thus, a lower effective tax rate. Consequently, firms whose products are exempt from sales tax or taxed with **low statutory rates** have low incentives to evade. Likewise, as the share of their exports increases, exporter firms bear decreasing incentives to evade taxes because a larger portion of their sales is exempt from sales tax, reducing the effective sales tax rate.

On the other hand, the total amount paid by the firm as sales tax depends on the statutory tax rate of each of its inputs, including imports. **Imports**, in contrast to exports, are **not exempt**. Hence, the composition of the foreign and domestic inputs does not affect the effective sales tax rate, nor the incentives to evade. However, the tax system imposed a zero sales tax rate on **unprocessed primary inputs**, such as forestry, mining, fishing, and agriculture. Therefore, firms consuming a high share of primary inputs face a higher effective sales tax rate and thus, greater incentives to evade. 

Note that the effective sales tax rate might naturally be **negative** for firms in certain industries. Before the 1983 reform in Colombia, there were four different statutory sales tax rates: 4, 10, 15 and 25 percent. Because the sales tax was applied at the product level, *the total amount paid as sales tax by the firms on its inputs could be larger than the total amount charged by the firm as sales tax on its products.* This situation would result in a negative effective sales tax rate. Firms in this situation would receive a refund from the tax authority. 

Would firms with negative effective tax rates have incentives to overreport inputs to increase their refunds? Unlikely. Although the refunds had to be made within 30 days, *the procedure was complicated, and the tax authority delayed, on average, one year to process the payment*. Suspicion of fraudulent activities might further delay the process. Therefore, firms in this situation did not have incentives to overreport inputs to increase their refunds. 

<!-- (On the contrary, firms with negative effective tax rates would have incentives to *underreport* inputs to reduce the risk of being audited due to the refunds. These firms would be *better off reporting enough inputs to offset the sales tax charged on their products, thus avoiding the complications of refunds and potential audits*. This might explain the negative coefficients found in the statistical test in the empirical section of this paper. Why? Because corporations have incentives to report truthfully their inputs, not only because they are subject to harder scrutiny by the tax authority, but also because they would not like to reduce their profits artificially; profits influence the value of their shares, and thus, the wealth of their shareholders.

Underreporting inputs is the only reasonable explanation of the significantly negative coefficients found in the statistical test of tax evasion. Neither market power nor technology differences could explain the negative coefficients. Both market power on either side and technology differences would result in a smaller input cost share of revenues. 

Market power in the sales market implies that firms can sell at higher prices, increasing the denominator of the share, resulting in a smaller share. Market power in the buying market implies firms can buy inputs at lower prices, decreasing the numerator of the share, leading to smaller shares, too. Because corporations are more likely to have market power, their smaller share would lead to a positive coefficient in the statistical test and smaller output elasticity of inputs.

Likewise, firms with better technology are more likely to be more efficient in using inputs, resulting in smaller input costs relative to revenues. Because corporations are more likely to have better technology, their smaller share would lead to a positive coefficient in the statistical test and smaller output elasticity of inputs. Therefore, the negative coefficients found in the statistical test cannot be explained by market power or technology differences, but rather by firms with negative effective tax rates underreporting their inputs to avoid complications with refunds and potential audits.) -->

Whether firms in certain industries have incentives to overreport their inputs to evade sales taxes might **not** be **obvious** *ex-ante*. The tax code might be complex, with many exemptions and different statutory rates. Different taxes might generate overlapping or conflicting incentives. Available data might lack details on the products or inputs used by firms, making it difficult to identify the effective sales tax rate.

A first contribution of this paper is to provide practitioners and policymakers a way to identify industries where tax evasion through cost-overreporting might be non-trivial and can be identified from data. The simple model employed in this paper to investigate the mechanisms of tax evasion provides conditions that can be tested with data. As a result, I propose a statistical test where the null hypothesis states that firms in an industry of interest do not evade sales taxes by overreporting; the alternative states that firms do commit tax evasion [@sec-tax-ev-test].

Failing to reject the null hypothesis does not necessarily imply that firms in this industry are not overreporting. If a researcher suspects this practcie on a particular industry, he would have to investigate if the assumptions of the model are not unreasonable for said industry. The main assumption comes from the production function method, even though they might differ in their productivity, evaders and non-evaders share a common technology. 

With this in mind, in any dataset using SIC codes, it should be considered that the SIC codes groups firms with similar products, but some categories might group products that require different technologies. Furthermore, most firms are multiproducts, and might be classified under a certain SIC code because it produces more of a certain product marginally.

### Showing the Evidence 


```{r}
#| label: tbl-ielas-top5
#| tbl-cap: Intermediate elasticities for Corporations (Non-Evaders) and non-Corporations (Evaders) for different industries. Estimates were obtained using GNR (2020) method assuming a CD functional form. Intermediates are defined as raw materials. $\varepsilon$ is defined as **measurement error**. The Tax Evasion Test displays the coefficient of the statistical test, where the null hypothesis states that there is no tax evasion through cost overreporting. Among the industry characteristics, Sales is the industry's market share of the total sales in Colombia between 1981 and 1991. Sales Tax Rate is the average sales tax reported rate. Exports is the average share of exports of the industry total sales, and Exporters is the share of firms exporting 10 percent or more of their total sales. Bias-corrected bootstrap confidence intervals at 95% significanve level are displayed in brackets. \\*, \\*\\*, \\*\\*\\* denote significance at the 10%, 5%, and 1% levels (one-sided).

load("../Code/Products/i_elas.RData")

# col_names <- c("SIC", "Corps.", 
#         "Others","Tax Ev.","N","N (Corps.)","Sales (Mkt %)", "Effective", "Sales","Purchases","N (%)","Qty. (Avg. %)","N (%) ","Qty. (Avg. %) ")

col_names <- c("SIC", "Corps.", 
        "Others","Tax Ev.","N","N (Corps.)","Sales (Mkt %)", "Effective", "Sales","Purchases")

main_tbl %>% 
    mutate(
        across(n:share_imports_materials, ~replace(.x, type=="CI", NaN))
    ) %>%
    filter(
        sic_3 %in% top_10_revenue$sic_3[1:5]
    ) %>%
    select(
        sic_3, corps:mean_V_log_mats_share, n, n_Corp, sales, effective_tax_rate:purchases_sales_tax,
        # exporters:share_imports_materials
    ) %>%
    kbl(
        # digits = 2,
        align = "c",
        col.names = col_names,
        table.attr = 'data-quarto-disable-processing="true"'
    ) %>%
    # column_spec(2:4, width = "9em") %>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    add_header_above(
        c(" "=1, "Elasticities"=2, "Test"=1, " "=3, "Sales Tax Rate"=3)#, "Exports"=2, "Imports"=2)
    ) %>%
    collapse_rows(columns = 1, valign = "top") #%>%
    # pack_rows(
    #     index = c(
    #         "31 Food & Beverages" = 6,
    #         "32 Textile, Apparel & Leather" = 8,
    #         "33 Wood & Wood Products" = 4,
    #         "34 Paper & Printing" = 4,
    #         "35 Chemicals, Petroleum, Rubber & Plastic" = 6,
    #         "36 Non-Metallic Mineral Products" = 2,
    #         # "37 Basic Metals" = 4,
    #         "38 Fabricated Metal Products, Machinery & Equipment" = 8,
    #         "39 Other Manufacturing" = 2
    #     )
    # )
    

```

```{r}
#| label: tbl-ielas
#| tbl-cap: Intermediate elasticities for Corporations (Non-Evaders) and non-Corporations (Evaders) for different industries. Estimates were obtained using GNR (2020) method assuming a CD functional form. Intermediates are defined as raw materials. $\varepsilon$ is defined as **measurement error**. The Tax Evasion Test displays the coefficient of the statistical test, where the null hypothesis states that there is no tax evasion through cost overreporting. Among the industry characteristics, Sales is the industry's market share of the total sales in Colombia between 1981 and 1991. Sales Tax Rate is the average sales tax reported rate. Exports is the average share of exports of the industry total sales, and Exporters is the share of firms exporting 10 percent or more of their total sales. Bias-corrected bootstrap confidence intervals at 95% significanve level are displayed in brackets. \\*, \\*\\*, \\*\\*\\* denote significance at the 10%, 5%, and 1% levels (one-sided).

load("../Code/Products/i_elas.RData")

# col_names <- c("SIC", "Corps.", 
#         "Others","Tax Ev.","N","N (Corps.)","Sales (Mkt %)", "Effective", "Sales","Purchases","N (%)","Qty. (Avg. %)","N (%) ","Qty. (Avg. %) ")

main_tbl %>% 
    mutate(
        across(n:share_imports_materials, ~replace(.x, type=="CI", NaN))
    ) %>%
    select(
        sic_3, corps:mean_V_log_mats_share, n, n_Corp, sales, effective_tax_rate:purchases_sales_tax,
        # exporters:share_imports_materials
    ) %>%
    kbl(
        # digits = 2,
        align = "c",
        col.names = col_names,
        table.attr = 'data-quarto-disable-processing="true"'
    ) %>%
    # column_spec(2:4, width = "9em") %>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    add_header_above(
        c(" "=1, "Elasticities"=2, "Test"=1, " "=3, "Sales Tax Rate"=3)#, "Exports"=2, "Imports"=2)
    ) %>%
    collapse_rows(columns = 1, valign = "top") %>%
    pack_rows(
        index = c(
            "31 Food & Beverages" = 6,
            "32 Textile, Apparel & Leather" = 8,
            "33 Wood & Wood Products" = 4,
            "34 Paper & Printing" = 4,
            "35 Chemicals, Petroleum, Rubber & Plastic" = 6,
            "36 Non-Metallic Mineral Products" = 2,
            # "37 Basic Metals" = 4,
            "38 Fabricated Metal Products, Machinery & Equipment" = 8,
            "39 Other Manufacturing" = 2
        )
    )
    

```

31 Food & Beverages:

- 311 Food Products (Meat, Dairy, Sugar, Bakery, etc.)
- 312 Food Products (Animal feeds, Others)
- 313 Beverages (Soft drinks, Alcoholic beverages, etc.)

In the Food and Beverages industry classification, industry 313 beverges displays suspicious activity of overreporting. This finding is consistent with the model because, in contrast to 311 and 312, industry 313 is not exempt from the sales tax. In fact, the effective sales tax rate for industries 311 and 312 is negative, implying that these firms were receving refunds from the government. In comparison, industries in 313 industry would have higher incentives to overreport because of their positive effective sales tax. 

32 Textile, Apparel & Leather: 

- 321 Textiles
- 322 Wearing apparel
- 323 Leather and Fur Products
- 324 Footwear

@tbl-ielas also shows evidence for potential tax evasion by overreporting in industries 321, 322, and 324. Again, from the theory perspective, these firms face positie effective tax rates, tax rates generate incentives to evade. This is consistent with the model. Corporations in industries 321, 322, and 324 display intermediate elasticities statistically smaller than the rest of the firms and the tax evasion test display a significantly positive coefficient.

What about industry 323? The effective sales tax rate is positive but does not display evidence of evasion according to the test, moreover the coefficient of the test is negative and statistically significant as indicated by the confidence intervals. 

Most likely, it is not a good idea to compare corporations with the rest of the firms in this industry. First, looking at the sample size, we note that the number of corporations in this industry is small. While this is also true for industry 324, looking more closely, we can also note that industry 323 groups classifications 3231 (Leather Tanning and Finishing), 3232 (Fur dressing and Dyeing), and 3233 (Leather products, except footwear and wearing apparel). In contrast, industry 324, only includes 3240 (Footwear, except plastic). The two most important groups of 323 are 3231 (30% of all the firms) and 3233 (60%). However, the composition of these subindustries is different between corporations (60/40) and non-corporations (22/73). 

Although technologies between small and large firms were similar at the core, the processes were significantly different which raises the question on the validity of the comparision between corporations and the other firms. During this period, small firms were tipically artisanal producers. These smaller establishments relied primarily on traditional local tanning methods based on vegetable extracts such as quebracho and chestnut. The process is long, typically requiring several weeks, however the products are highly valued because their durability and the distinctive patina it acquires as it ages. Their products were destined for the local market. 

In contrast, large firms used a chrome-based mineral tanning, mechanized drums and automated finishing machinery. Chromium tanning is faster and allows for mass scale consistent quality. The product is softer and water resistant. These characteristics make chrome-based tanning leather suitable for exporting to the US and European markets. However, chromium disposal requires advanced waste water treatment necessary to remove havey metals and prevent chromium discharge into the environment. Furthermore, these firms need to comply with strict enviromental regulations including regular monitoring, hazard assessment, and reporting. 

The data shows that corporations are more oriented to the foreign market than the rest of the firms, with highest average share of exports (28 vs. 13%), highest share of exporters (80 vs 35%).


33 Wood & Wood Products; 34 Paper & Printing:

- 331 Wood Products except furniture (Sawmills, Containers, etc.)
- 332 Wood Furniture (Wooden furniture and fixtures)
- 341 Paper and Paper Products
- 342 Printing, publishing and allied industries

In these categories, we find that industries 331 and 342 display suspicious activity of overreporting. However, results should be taken with caution in particular for industry 331 because the sample of corporations is relatively small.

Again, failing to reject the null hypothesis of no tax evasion could only mean that cost overreporting cannot be identfied with the data available using corporations as reference group. 

<!-- Both industries sell their products locally (low shares of exports) and one third of their joint consumption comes from forestry, which is exempt of sales tax (IO-Matrix 1985 Colombia). For industry 331, the large share of primary goods probably leads to a high effective sales tax rate because we expect there might not be many more other inputs needed in the production process. Hence, firms in this industry might face high incentives to overreport their non-primary inputs to evade sales taxes.

However, for firms in industry 332, even though they also consume a large share of primary goods, they also consume a more diverse set of inputs to produce the wood furniture, such as textiles, chemicals, foam cushions, and others. Because of this wide range of inputs, the sales tax paid for their inputs might be high leading to a low effective sales rate and hence, low incentives to evade taxes. -->


35 Chemicals, Petroleum, Rubber & Plastic; 36 Non-Metallic Mineral Products:

- 351 Industrial Chemicals (Basic chemicals, Fertilizers, Synthetic resins and fibers)
- 352 Other Chemicals (Paints and lacquers, Drugs, Soap and cosmetics, etc.)
- 356 Other Plastic Products (not classified elsewhere)
- 369 Non-Metallic Mineral Products (Structural clay products, Cement and plaster, Other non-metallic mineral products)

I find significant evidence for industry 369 Non-Metallic Mineral Products, and some evidence for industry 352. Results should be taken with caution as both industries include different types of products, processes might vary significantly from one another. On the other hand, the sample of corporations is not small and there are observations across all subindustries, suggesting that the comparison between corporations and the rest of the firms might not be unreasonable.

Regarding industry 356, the perspicaz reader might notice that the coefficient of the tax evasion test is negative and statistically significant. However, in this category is not clear the composition of the subcategories included, as it covers other plastic products not classfied elsewhere. Unlike other categories, this one only includes one subcategory, 3560 (Plastic products, not elsewhere classified). As in other industries, corporations have higher average share of exports and their share of exporters is higher than the non-incorporated firms. Does this matter? Likely. How? It is not clear.

38 Fabricated Metal Products, Machinery & Equipment; 39 Other Manufacturing:

- 381 Fabricated Metal Products (Structural metal products, Cutlery, Hand tools, etc.)
- 382 Machinery and Equipment (Agricultural machinery, Metalworking machinery, etc.)
- 383 Electrical Machinery and Apparatus (Electric motors, Generators, etc.)
- 384 Transport Equipment (Motor vehicles, Aircraft, Ships, etc.)
- 390 Other Manufacturing (Jewelry, Musical instruments, etc.)

I cannot reject the null hypothesis of no tax evasion by overreporting for these industries. It is interesting to note that agricultural machinery, transportation equipment, and equipment were exempt from sales tax since 1974. In 1984, exemptions for agricultural machinery and transportation equipment were removed. 

If these results are valid, this could imply that there is a dynamic component to the tax evasion decision. Meaning that the desicion of tax evasion in the current period depends critically on the past periodl. For example, if a firm did not evade in the previous year, it might be less likely to evade in the current year. The fact that there is no evidence of tax evasion might suggest that this effect is persistent over time. 

How does this dynamic decision could enter the economic model? Firms in the agricultural machinery and transportation equipment sectors started facing incentives to evade after 1984. However, they have been providing truthful information to the tax authority for over a decade. They know that the probability of detection for them is high, given that the authority can easily compare their records with previous years and detect anomalies.

#### Results Summary

I find that four out of the top five (nine of the to top twenty) industries display activities consistent with tax evasion through cost overreporting in Colombia between 1981 and 1991. Firms might overreport up to 22 percent of their costs. Consisten with the model, firms in industries with exempt products and negative effective sales tax rates display minor or no evidence of tax evasion. Furthermore, the evidence could suggest that the tax evasion decision is dynamic, as there is a lack of evidence of tax evasion in industries that lost exemption after a decade. 

Of course, the results should be taken with the usual precautions. The main assumption of the model is that evaders and non-evaders share a common technology. This assumption might be not unreasonable in most cases. However, commonly available data might group firms with similar products, but the technological processes might differ. 

On the other hand, failing to reject the null hypothesis of no tax evasion does not necessarily mean that firms in this industry are not overreporting; it might mean that overreporting cannot be identified with the data available at this industry level using corporations as the reference group. A researcher suspecting tax evasion in a particular industry should exhaustively investigate if the assumptions of the model are not unreasonable for said industry. In particular, she should inform herself about the industry technological processeses and asses if evaders and non-evaders can be compared.


::: {#fig-io-mat-1985}

![IO-Matrix 1985 Colombia](images/tables/COL-Mat-InsProd-1985.pdf){width="90%"}

:::

<!-- 

In practice, the situation is far more intricate. First, firms are actively trying to conceal their fraudulent activities, rendering the detection of tax evasion non-trivial. Second, firms face other taxes and exemptions. In cases where the tax code complexity is significant due to the variety of additional taxes, intricate exemptions, and frequent reforms, this might result in overlapping or potentially conflicting incentives. For example, in Colombia, firms are also subject to corporate income taxes that vary by type of juridical organization. Limited liability companies, for instance, faced a 20 percent income tax while 

In Colombia, firms are subject also to corporate income taxes depending on the type of firm (known as juridical organization in Colombia), property taxes among others at the federal level, steel taxes, other taxes. Municipalities also imposed additional taxes on the firms. The complexities of the colombian tax code resulted in double taxation of individuals. An issue that the frequent reforms tried to address.

In practice, the landscape is far more intricate. Firms go to great lengths to obscure fraudulent activities, making tax evasion detection a formidable challenge. Beyond sales taxes, firms face a web of additional taxes that create overlapping and sometimes conflicting incentives. For instance, in Colombia during the study period, the tax system was not only complex but also frequently reformed. Firms were liable for corporate income taxes that varied by juridical organization, property taxes, and sector-specific levies such as steel taxes. Municipalities layered on their own taxes, further complicating compliance. This patchwork of regulations often resulted in double taxation for individuals—a persistent problem that successive reforms attempted to resolve. For example, a manufacturing firm exporting goods might benefit from sales tax exemptions on exports, but still face high municipal taxes and sector-specific levies, creating a mix of incentives that influence both tax compliance and evasion strategies.

First, because it might not be obvious what industries might be the most affected. Altough theory provides some clues, firms face a plethora of other taxes that might create conflicting incentives. The situation might be worsened if the tax authorities are frequently tinkering with the tax system. 

 -->


```{r}
#| label: tbl-comp-test
#| tbl-cap: Comparison of different methods to estimate the bias corrected confidence intervals and the p-values. The null hypothesis states that firms do not commit tax evasion through cost-overreporting. The alternative is that they do. The first column is a difference of the means test (includes error of the estimator, but assumes independence of the samples). The different methods showon in the rest of the columns are combinations of two different procedures when sampling the bootstrap —sampling from corporations and non-corporations, or sampling full data— and two different methods to estimate the coefficient of the test — using all the firms or only the non-incorporated firms. When not fixing the number of corporations, Bayesian sampling was used to ensure there would be at least one corporation needed to estimate the first-stage parameter. The numbers in parenthesis are the standard errors of the mean difference test. The numbers in brackets represent the bias-corrected bootstrap confidence intervals at 95% significance level. \\*, \\*\\*, \\*\\*\\* denote significance at the 10%, 5%, and 1% levels (one-sided).

load("../Code/Products/tests_tbl.RData")

tests_tbl[-2] %>%
    kbl(
        # digits = 3,
        # align = "c",
        table.attr = 'data-quarto-disable-processing="true"',
        col.names = c("SIC", "Mean Diff.","All", "Others","All ","Others ")
    ) %>%
    # column_spec(1, width = "10em") %>%
    # column_spec(2:4, width = "7em") %>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    add_header_above(
        c(" "=2, "Two Group Sampling"=2, "Bayesian"=2)
    ) %>%
    add_header_above(
        c(" "=2, "Bootstrap"=4)
    ) %>%
    collapse_rows(columns = 1, valign = "top")

```


```{r}
#| label: tbl-sec11-inds-char-coprs-vs-others
#| tbl-cap: Comparison of industry characteristics between corporations and non-corporations.

# load("../Code/Products/i_elas.RData")

names_header <- c("N", "Avg. Age", "Sales (Sales Tax Rate)", "Purchases (Sales Tax Rate)", "Mkt % (Sales)", "Exports (Avg. %)", "Imports (Avg. %)", "Exporters (N %)", "Importers (N %)")

header <- rep(2, length(names_header))
names(header) <- names_header

inds_char_tbl_corp %>%
    kbl(
        table.attr = 'data-quarto-disable-processing="true"',
        col.names = c("SIC", rep(c("Corp's", "Others"), 9))
    ) %>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    add_header_above(
        c(" "=1, header)
    )

```

```{r}
#| label: tbl-tims-test
#| tbl-cap: Rejection frequencies of the $\mathcal{V}_{it}$ for Corporations and Non-Corporations. The rejection frequencies of the one tail test are the average number of observations that fell above the 95\% region of the $f_{\varepsilon}(\varepsilon)$ distribution recovered in the first stage. The rejection frequencies of the two tail test are the average number of observations that fell above the 97.5\% or below the 2.5\% region. 

load("../Code/Products/tims-test.RData")

tims_tst_tbl %>%
    kbl(
        table.attr = 'data-quarto-disable-processing="true"',
        col.names = c("SIC", "Corp","Non-Corp","Corp ","Non-Corp ")
    ) %>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    collapse_rows(columns = 1, valign = "top") %>%
    add_header_above(
        c(" "=1, "One Tail"=2, "Two Tail"=2)
    ) 

```