### Data

The data is a well-known data set that has been used in the estimation of production functions and productivity before. The dataset comes from the Annual Survey of Manufacturing (EAM) and contains information about manufacturing firms with more than 10 employees from 1981 to 1991.

Besides the information on output, intermediates, capital, and labor, the dataset includes the type of juridical organization, the sales taxes, and the metropolitan area and country region.

```{r}
#| label: fig-revenue-hist-bunch-0
#| fig-cap: Revenue distribution Juridical Org. 0 (81-83)
#| echo: false
#| warning: false

library(tidyverse)
library(ggplot2)
library(modeest)
library(fixest)
library(kableExtra)

load("../Code/Products/colombia_data.RData")
load("../Code/Products/global_vars.RData")
colombia_data_frame %>%
    filter(
        year<=83,
        juridical_organization==0
    ) %>%
    pull(sales) %>%
    hist(., 
    breaks=30000,
    xlim=c(0,5000),
    main="")
abline(v=real_tax_tresh_1983)
title("")

```

```{r}
#| label: fig-revenue-hist-bunch-1
#| fig-cap: Revenue distribution Juridical Org. 1 (81-83)
#| echo: false
#| warning: false

# library(tidyverse)
# library(ggplot2)
# library(modeest)
# library(fixest)

# load("../Code/Products/colombia_data.RData")
# load("../Code/Products/global_vars.RData")
colombia_data_frame %>%
    filter(
        year<=83,
        juridical_organization==1
    ) %>%
    pull(sales) %>%
    hist(., 
    breaks=30000,
    xlim=c(0,5000),
    main="")
abline(v=real_tax_tresh_1983)
title("")

```

$$
log(s_{it})= \Phi(k_{it},l_{it},m_{it})+ \alpha_1Tax_{it}+\mathbf{\beta}_1'JurOrg_i + \beta_2'JurOrg_i\times\gamma_t+ \gamma_t + \gamma_{ind} +\gamma_{metro} + \varepsilon_{it}
$$ {#eq-reg-tax-jo}


::: {#tbl-reg-jo-tax}
```{r}
#| echo: false
#| warning: false
#| results: asis

setFixest_etable(markdown = TRUE)

setFixest_dict(c(
    share_sales_tax = "Sales Tax Rate",
    `relevel(factor(juridical_organization),ref="9")0` = "J. Org. (0)",
    `relevel(factor(juridical_organization),ref="9")1` = "J. Org. (1)",
    `relevel(factor(juridical_organization),ref="9")2` = "J. Org. (2)",
    `relevel(factor(juridical_organization),ref="9")3` = "J. Org. (3)",
    `relevel(factor(juridical_organization),ref="9")4` = "J. Org. (4)",
    `relevel(factor(juridical_organization),ref="9")5` = "J. Org. (5)",
    `relevel(factor(juridical_organization),ref="9")6` = "J. Org. (6)",
    `relevel(factor(juridical_organization),ref="9")7` = "J. Org. (7)",
    `relevel(factor(juridical_organization),ref="9")8` = "J. Org. (8)",
    `polym(m,k,l,degree=2,raw=TRUE)1.0.0` = "\\(m\\)",
    `polym(m,k,l,degree=2,raw=TRUE)2.0.0` = "\\(m^2\\)",
    `polym(m,k,l,degree=2,raw=TRUE)0.1.0` = "\\(k\\)",
    `polym(m,k,l,degree=2,raw=TRUE)0.2.0` = "\\(k^2\\)",
    `polym(m,k,l,degree=2,raw=TRUE)0.0.1` = "\\(l\\)",
    `polym(m,k,l,degree=2,raw=TRUE)0.0.2` = "\\(l^2\\)",
    `polym(m,k,l,degree=2,raw=TRUE)1.1.0` = "\\(mk\\)",
    `polym(m,k,l,degree=2,raw=TRUE)1.0.1` = "\\(ml\\)",
    `polym(m,k,l,degree=2,raw=TRUE)0.1.1` = "\\(kl\\)",
    log_share = "\\(log(s)\\)",
    sic_3 = "Industry",
    year = "Year",
    `log(energy/sales)` = "\\(log(Energy/Revenue)\\)",
    `log(mats_serv/sales)` = "\\(log(Mats+Serv/Revenue)\\)",
    metro_area_code = "Metro Area",
    `factor(fiscal_period)83` = "84-86 F.P.",
    `factor(fiscal_period)86` = "87-91 F.P."#,
    # "note 1" = "Reference group is J.O. (9) in 1981. Production Function Polynomial and interactions not displayed.",
    # "note 2" = "Reference group is J.O. (9) in Fiscal Period 1981-1983. Only interactions displayed."
))

feols(
        log_share ~  polym(m, k, l, degree = 2, raw = TRUE)+share_sales_tax+relevel(factor(juridical_organization),ref="9")*factor(year)|csw0(sic_3,metro_area_code),
        data = colombia_data_frame, cluster=~sic_3+year
    ) |> etable(
        keep = c("Sales","J. Org."),
        drop="year",
        notes = "Reference group is J.O. (9) in 1981."
        # headers = c("(1)","(2)","(3)","(4)")#,
        # postprocess.df = pandoc.table.return, style = "rmarkdown"
    ) 
    # |> kbl(
    #     escape = FALSE
    # )

```

Juridical Organization type and Sales Tax effect on the log share of intermediate inputs.
:::

$$
log(s_{it})= \Phi(k_{it},l_{it},m_{it})+ \beta_1'JurOrg_i + \beta_2'FiscalPd+\beta_2'JurOrg_i\times FiscalPd + \gamma_t + \gamma_{ind} +\gamma_{metro} + \varepsilon_{it}
$$ {#eq-reg-tax-fp}

::: {#tbl-reg-fiscal-p}
```{r}
#| echo: false
#| warning: false
#| results: asis


colombia_data_frame %>%
    ungroup() %>%
    mutate(
        fiscal_period = case_when(
            year <= 83 ~ '74',
            year <= 86 ~ '83',
            .default = '86'
        )
    ) %>%
    feols(
        log_share ~ polym(m, k, l, degree = 2, raw = TRUE)+relevel(factor(juridical_organization), ref="9")*factor(fiscal_period)| csw0(sic_3,metro_area_code,year),#factor(sic_3)+factor(metro_area_code)+factor(year),
        data = . , cluster = ~sic_3+year
    ) %>%
    etable(
        keep = "%:",
        notes = "Reference group is J.O. (9) in Fiscal Period 1981-1983."
        # tex = TRUE
        # headers = c("(1)","(2)","(3)","(4)")
    ) 
    # %>%
    # kbl(
    #     escape = FALSE
    # )
    


```

Juridical Organization type per fiscal period effect on the log share of intermediate inputs.
:::

::: {#tbl-reg-energy}
```{r}
#| echo: false
#| warning: false
#| results: asis

colombia_data_frame %>%
    feols(
        log(energy/sales) ~ polym(mats_serv, k, l,log(energy), degree = 2, raw = TRUE)+share_sales_tax+
        relevel(factor(juridical_organization), ref="9")*factor(year) | csw0(sic_3,metro_area_code),
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        keep = c("Sales","J. Org."),
        drop="year",
        notes = "Reference group is J.O. (9) in 1981."
    )


```
Juridical Organization type and Sales Tax effect on the log share of Consumed Energy.
:::

::: {#tbl-reg-mats}
```{r}
#| echo: false
#| warning: false
#| results: asis


colombia_data_frame %>%
    feols(
        log(mats_serv/sales) ~ polym(mats_serv, k, l,log(energy), degree = 2, raw = TRUE)+share_sales_tax+
        relevel(factor(juridical_organization), ref="9")*factor(year) | csw0(sic_3,metro_area_code),
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        keep = c("Sales","J. Org."),
        drop="year",
        notes = "Reference group is J.O. (9) in 1981."
    )

```

Juridical Organization type and Sales Tax effect on the log share of Raw Materials and Services.
:::