### Data

The data is a well-known data set that has been used in the estimation of production functions and productivity before. The dataset comes from the Annual Survey of Manufacturing (EAM) and contains information about manufacturing firms with more than 10 employees from 1981 to 1991.

Besides the information on output, intermediates, capital, and labor, the dataset includes the type of juridical organization, the sales taxes, and the metropolitan area and country region.

```{r}
#| label: fig-revenue-hist-bunch-0
#| fig-cap: Revenue distribution Proprietorships (81-83)
#| cap-location: top
#| echo: false
#| warning: false


colombia_data_frame %>%
    filter(
        year<=83,
        juridical_organization==0
    ) %>%
    pull(sales) %>%
    hist(., 
    breaks=30000,
    xlim=c(0,5000),
    main="")
abline(v=real_tax_tresh_1983)
title("")

```

```{r}
#| label: fig-revenue-hist-bunch-1
#| fig-cap: Revenue distribution Limited Partnership (81-83)
#| cap-location: top
#| echo: false
#| warning: false

# library(tidyverse)
# library(ggplot2)
# library(modeest)
# library(fixest)

# load("../Code/Products/colombia_data.RData")
# load("../Code/Products/global_vars.RData")
colombia_data_frame %>%
    filter(
        year<=83,
        juridical_organization==1
    ) %>%
    pull(sales) %>%
    hist(., 
    breaks=30000,
    xlim=c(0,5000),
    main="")
abline(v=real_tax_tresh_1983)
title("")

```

$$
log(s_{it})= \Phi(k_{it},l_{it},m_{it})+ \alpha_1Tax_{it}+\mathbf{\beta}_1'JurOrg_i + \beta_2'JurOrg_i\times\gamma_t+ \gamma_t + \gamma_{ind} +\gamma_{metro} + \varepsilon_{it}
$$ {#eq-reg-tax-jo}


::: {#tbl-reg-jo-tax layout-ncol=1}

```{r}
#| eval: true
#| echo: false
#| warning: false
#| results: asis

colombia_data_frame %>%
    feols( log_share ~ share_sales_tax+
        relevel(factor(juridical_organization),ref="3")*factor(year)+
        polym(m, k, l, degree = 2, raw = TRUE)
        | csw0(sic_3,metro_area_code),
        data = ., cluster=~sic_3+year
    ) %>% 
    etable(
        drop = c("Year", "%poly", "Const"),
        notes = "Reference group is Corporations in 1981.",
        div.class = "table"
    ) 


```


Effect of the Juridical Organization Type and Sales Tax on the Log Share of Intermediate Inputs.

:::

$$
log(s_{it})= \Phi(k_{it},l_{it},m_{it})+ \beta_1'JurOrg_i + \beta_2'FiscalPd+\beta_2'JurOrg_i\times FiscalPd + \gamma_t + \gamma_{ind} +\gamma_{metro} + \varepsilon_{it}
$$ {#eq-reg-tax-fp}

::: {#tbl-reg-fiscal-p layout-ncol=1}

```{r}
#| echo: false
#| warning: false
#| results: asis


colombia_data_frame %>%
    ungroup() %>%
    mutate(
        fiscal_period = case_when(
            year <= 83 ~ '74',
            year <= 86 ~ '83',
            .default = '86'
        )
    ) %>%
    feols(
        log_share ~ polym(m, k, l, degree = 2, raw = TRUE)+relevel(factor(juridical_organization), ref="3")*factor(year)| csw0(sic_3,metro_area_code),#factor(sic_3)+factor(metro_area_code)+factor(year),
        data = . , cluster = ~sic_3+year
    ) %>%
    etable(
        keep = "Proprietorship",
        # drop = "%:",
        notes = "Reference group is Corporations in 1981",
        div.class = "table"
        # tex = TRUE
        # headers = c("(1)","(2)","(3)","(4)")
    ) 
    # %>%
    # kbl(
    #     escape = FALSE
    # )
    


```

Effect of the Type of Juridical Organization on the Log Share of Intermediate Inputs, per Fiscal Period.

:::

::: {#tbl-reg-energy layout-ncol=1}

```{r}
#| echo: false
#| warning: false
#| results: asis

colombia_data_frame %>%
    feols(
        log(consumed_energy/sales) ~ share_sales_tax+
        relevel(factor(juridical_organization), ref="3")*factor(year)+polym(log(mats_serv), k, l,log(consumed_energy), degree = 2, raw = TRUE) | csw0(sic_3,metro_area_code),
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        # keep = c("Proprietorship"),
        drop=c("Year","%:","%polym","Const"),
        notes = "Reference group is Corporations in 1981.",
        div.class = "table"
    )


```

Effect of the Juridical Organization Type and Sales Tax on the Log Share of Consumed Energy.

:::

::: {#tbl-reg-ded layout-ncol=1}

```{r}
#| echo: false
#| warning: false
#| results: asis


colombia_data_frame %>%
    mutate(
        deductibles = materials+deductible_expenses,
        non_deductibles = consumed_energy+non_deductible_expenses
    ) %>%
    feols(
        log(deductibles/sales) ~ share_sales_tax+
        relevel(factor(juridical_organization), ref="3")*factor(year)+polym(log(deductibles), k, l,log(non_deductibles), degree = 2, raw = TRUE) | csw0(sic_3,metro_area_code),
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        # keep = c("Sales","J. Org."),
        # markdown = NULL,
        # tex = FALSE,
        drop=c("Year","%:","%polym","Const"),
        notes = "Reference group is Corporations in 1981.",
        div.class = "table"
    ) 
    # %>%
    # kbl(
    #     # format = "html"
    #     table.attr = 'data-quarto-disable-processing="true"'
    # )%>%
    # kable_classic(full_width=F, html_font = "Cambria")

```

Effect of the Juridical Organization Type and Sales Tax on the Log Share of Deductible Expenses.

:::

::: {#tbl-reg-non-ded layout-ncol=1}

```{r}
#| echo: false
#| warning: false
#| results: asis


colombia_data_frame %>%
    mutate(
        deductibles = materials+deductible_expenses,
        non_deductibles = consumed_energy+non_deductible_expenses
    ) %>%
    feols(
        log(non_deductibles/sales) ~ share_sales_tax+
        relevel(factor(juridical_organization), ref="3")*factor(year)+polym(log(deductibles), k, l,log(non_deductibles), degree = 2, raw = TRUE) | csw0(sic_3,metro_area_code),
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        # keep = c("Sales","J. Org."),
        # markdown = NULL,
        # tex = FALSE,
        drop=c("Year","%:","%polym","Const"),
        notes = "Reference group is Corporations in 1981.",
        div.class = "table"
    ) 
    # %>%
    # kbl(
    #     # format = "html"
    #     table.attr = 'data-quarto-disable-processing="true"'
    # )%>%
    # kable_classic(full_width=F, html_font = "Cambria")

```

Effect of the Juridical Organization Type and Sales Tax on the Log Share of Non-Deductible Expenses.

:::