### Do Corporations in Colombia have different technologies than other juridical organizations?

The evidence suggests that Corporations have similar technologies to the rest of the firms. I look at the share of revenues of different input costs. In doing so, I consider the incentives generated by the fiscal environment in Colombia. Firms had the lowest incentives to evade taxes by misreporting capital, consumed energy, and skilled labor. The cost share of revenue of these inputs suggests that Corporations and the rest of the firms had the same technologies.

#### Capital

Firms could not deduct capital goods from sales taxes. However, firms of capital-intensive industries might have had incentives to underreport capital because capital was used to set the minimum income tax. Income tax could not be less than 8 percent of the capital.

#### Energy

Before the electrical energy reform in 1994, most of the market was supplied by municipality-owned companies with some participation of private firms. It is unlikely that firms overreported energy, as they have to purchase from a Corporation, or a municipality or region-owned company. Both of those organizations had no incentives to cooperate and provide fake invoices.

In the data, energy sold by corporations accounted on average for 73% of the total energy sold, but only 1.7% of the total energy purchased. In addition, corporations sold energy at 12 times the market price on average [@tbl-energy]. The high price might suggest corporations had market power in the electric energy market, however, this is unlikely to be relevant to affect any estimations as their overall market share is small.


```{r}
#| label: tbl-energy
#| tbl-cap: Electric energy market in Colombia (1981-1991).
#| echo: false
#| warning: false
#| eval: true


colombia_data_frame %>% 
    ungroup() %>%
    mutate(
        # sold_energy = purchased_energy+generated_energy-consumed_energy
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Community")
        ),
        total_energy_sold = sum(sold_energy, na.rm=TRUE),
        total_energy_purchased = sum(purchased_energy, na.rm = TRUE)
    ) %>%
    group_by(JO) %>% 
    summarise(
        # p_purchased = mean(p_energy_purchased, na.rm = TRUE), 
        p_sold_purchase = mean(p_energy_sold/p_energy_purchased, na.rm = TRUE),
        # mean_energy_sold = mean(sold_energy, na.rm = TRUE),
        # total_energy_sold_JO = sum(sold_energy, na.rm = TRUE),
        percent_energy_sold_JO = sum(sold_energy/total_energy_sold, na.rm = TRUE)*100,
        # mean_energy_purchased_JO = mean(purchased_energy, na.rm = TRUE),
        percent_energy_purchased_JO = sum(sold_energy/total_energy_purchased, na.rm = TRUE)*100,
        generated_energy_perc = mean(generated_energy/consumed_energy, na.rm=TRUE)*100
    ) %>%
    filter(is.na(JO)==FALSE) %>%
    kbl(
        # format = "html",
        digits = 1,
        table.attr = 'data-quarto-disable-processing="true"',
        col.names = c(
            '',
            'Sold/Purchased Price Ratio',
            'Sold Energy (% of Total Sold Energy)',
            'Sold Energy (% of Total Purchased Energy)',
            'Generated Energy (% of Consumed Energy)'
        )
    )%>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    collapse_rows(1, valign="top", latex_hline = "major")

```

#### Labor

Firms might have incentives to underreport labor to evade Payroll Taxes (PRT) if the expected benefits of evading the PRT outweigh the opportunity costs of evading Corporate Income Tax (CIT) by overreporting labor costs and the expected cost of evading PRT [@Almunia2018].

Firms are more likely to underreport unskilled rather than skilled labor. Skilled employees are less likely to cooperate with firms in underreporting their wages. Firms might offer employees cash compensations in order for employees to accept lower reported wages or report their wages at all. The cost for employees is that these payroll taxes provide them with social benefits such as social security or public health access. These benefits are not obvious in the short run. It is more likely that unskilled labor to be short-sighted and accept to cooperate with firms to underreport their wages. Skilled workers, on the other hand, are less likely to accept these conditions and to have outside options and move if the conditions are not favorable to them.

#### Services and other expenditures

The Colombian dataset allows, to some extent, separating expenditures, including services, into deductible and non-deductible expenses. In contrast to non-evading firms, evading firms should use a higher share of deductible expenses. The reason is that firms have incentives to overreport deductible expenditure to evade ICT and VAT.

The Colombian data separates firms' total expenditures into general and industrial expenditures. Industrial expenditure is defined as the indirect costs and expenditures incurred by the firm in order to perform its industrial activity. The data lists the purchase of accessories and replacement parts, fuels and lubricants consumed by the establishment, industrial work by other establishments, and third-party repairs and maintenance, among others, as industrial expenditures[^inds_exp]. All other expenses, including insurance (excluding employee benefits) and machinery rentals, are considered general expenses.

Most services were excluded from sales taxes. Some non-excluded services in this period were insurance premiums (excluding life insurance), repair and maintenance, national and international telegrams, telex, and telephone, and rental of goods and chattels, including financial leasing.

I classify as deductible expenses the following industrial expenditures: purchase of fuels and lubricants, payments to third parties for repair and maintenance, purchase of raw materials and goods sold without transformation; and the following general expenditures: machinery rental, insurance excluding employee benefits, and water, mail and telephone expenses.


[^inds_exp]: After 1992, industrial expenditure included rent of machinery and property, payment for professional services, insurance (excluding employee benefits), water, mail, and telephone.

#### Technical note

According to the notes on the dataset, the quantity of energy consumed by firms is estimated as the difference between purchased plus generated energy and sold energy. In contrast, the value of consumed energy is the difference between the value of purchased and sold energy. Consequently, using the calculated value over the calculated quantity of consumed energy ignores the quantity of generated energy and the increase in the price of sold energy by corporations.

In @Gandhi2020, services are defined as general expenditures minus machinery rental and interest payments. However, this approach does not include industrial expenditures which are closely linked to the production process. In the Colombian data, the intermediate consumption is defined as raw materials, purchased electric energy, and industrial expenditure. This definition is close to what is commonly defined as intermediate inputs.

#### Results

@tbl-reg-shares shows that in terms of the capital and consumed energy share of revenue, corporations are not different from other types of juridical organizations. Capital and consumed energy are reliable indicators that Corporations have similar technologies to other firms because firms have no incentives to overreport capital or consumed energy. On the other hand, the raw materials share of revenues is 3 percent higher for non-corporations. Firms have incentives to overreport raw materials to evade sales taxes and CIT. Hence, materials are not a good reference to compare technology between Corporations and other types of firms.

@tbl-reg-shares-2 shows that the skilled labor share of revenue for corporations is not statistically different from other types of firms. On the other hand, unskilled labor is significantly lower for non-corporations. Unskilled workers are more likely to cooperate with non-corporations to underreport their employment/wages. An alternative explanation is that corporations employ more unskilled workers because they are bigger. Therefore, skilled labor is a more reliable indicator of technology and shows that corporations have similar technology to other firms. 

@tbl-reg-shares-2 also shows that the total expenditure share of revenue is 8 percent lower for non-corporations on average. On one hand, this might be due to size. Corporations tend to be larger than non-corporations. However, the composition of the expenditure matters. 

@tbl-reg-shares-3 shows that the deductible expenses share of total expenditure is 6 percent significantly higher for non-corporations. This is not the case if we classify expenditures by industrial and general expenses. Services as defined in GNR, that is general expenses minus machinery rental and interest payments, as a share of total expenditure is 5 percent higher for non-corporations. Services include deductible expenses such as insurance excluding employee benefits, and telegrams and telephone services.

In summary, looking at the inputs that firms are less likely to misreport due to tax evasion incentives, the evidence suggests that Corporations have similar technologies to the other types of firms. In addition, I find that the cost share of inputs that are likely to be misreported due to tax evasion incentives are significantly different from corporations and in the expected direction. In particular, it looks like firms overreport materials and deductible expenses, and underreport unskilled labor.



```{r}
#| label: tbl-corp-vs-non-corp
#| tbl-cap: Comparison of different input over revenue ratios for Corporations and other types of Juridical Organizations.
#| echo: false
#| warning: false
#| eval: false
#| include: false


colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Comm.")
        ),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        `Corp.` = ifelse(juridical_organization==3,"Corp","Other"),
        mats_serv_share = mats_serv/sales,
        labor_employee_years_share = labor_employee_years/sales
    ) %>%
    group_by(sic_3,`Corp.`) %>%
    summarise( 
       across(
            ends_with("_share"),
            list(
                mean = ~mean(.x, na.rm = TRUE),
                sd = ~sd(.x, na.rm = TRUE)#/sqrt(n())*1.96
            )
        )
    ) %>%
    mutate(
        Energy  = str_glue("{round(consumed_energy_share_mean,1)} ({round(consumed_energy_share_sd,2)})"),
        Capital = str_glue(
            "{round(capital_share_mean,2)} ({round(capital_share_sd,2)})"
        ),
        Labor = str_glue(
            "{round(labor_employee_years_share_mean,2)} ({round(labor_employee_years_share_sd,2)})"
        ),
        `Skilled Labor` = str_glue(
            "{round(skilled_labor_share_mean,2)} ({round(skilled_labor_share_sd,2)})"
        ),
        `Unskilled Labor` = str_glue(
            "{round(unskilled_labor_share_mean,2)} ({round(unskilled_labor_share_sd,2)})"
        ),
        Industry = factor(sic_3)
    ) %>%
    ungroup() %>%
    select(
        Industry, `Corp.`, Energy, Capital, `Skilled Labor`, `Unskilled Labor`
    ) %>%
    kbl(
        # format = "html",
        table.attr = 'data-quarto-disable-processing="true"'
    )%>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    collapse_rows(1, valign="top", latex_hline = "major")



```

```{r}
#| label: tbl-corp-vs-non-exp
#| tbl-cap: Firms'expenses for Corporations and other types of Juridical Organizations by Industry.
#| echo: false
#| warning: FALSE
#| eval: false
#| include: false

colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Community")
        ),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        Corp = ifelse(juridical_organization==3,"Corp","Other"),
        mats_serv_share = mats_serv/sales,
        labor_employee_years_share = labor_employee_years/sales,
        gen_exp_share = general_expenditure/total_expenditure,
        inds_exp_share = industrial_expenditure/total_expenditure,
        non_deductible_expenses_share = non_deductible_expenses/total_expenditure,
        deductible_expenses_share = deductible_expenses/total_expenditure,
        inds_exp_non_deductible_share = inds_exp_non_deductible/industrial_expenditure,
        inds_exp_deductible_share = inds_exp_deductible/industrial_expenditure,
        total_expenses_share = total_expenditure/sales,
        serv_share = services/total_expenditure
    ) %>%
    group_by(sic_3,Corp) %>%
    summarise( 
       across(
            ends_with("_share"),
            list(
                mean = ~mean(.x, na.rm = TRUE),
                se = ~sd(.x, na.rm = TRUE)#/sqrt(n())#*1.96
            )
        )
    ) %>%
    mutate(
        `Total Expenditure` = str_glue(
            "{round(total_expenses_share_mean,2)} ({round(total_expenses_share_se,2)})"#,
            # .sep = "\n"
        ),
        `Services (GNR)` = str_glue(
            "{round(serv_share_mean,2)} ({round(serv_share_se,2)})"
        ),
        `General Exp.` = str_glue(
            "{round(gen_exp_share_mean,2)} ({round(gen_exp_share_se,2)})"
        ),
        `Industrial Exp.` = str_glue(
            "{round(inds_exp_share_mean,2)} ({round(inds_exp_share_se,2)})"
        ),
        `Deductible Exp.` = str_glue(
            "{round(deductible_expenses_share_mean,2)} ({round(deductible_expenses_share_se,2)})"
        ),
        `Deductible Inds. Exp.` = str_glue(
            "{round(inds_exp_deductible_share_mean,2)} ({round(inds_exp_deductible_share_se,2)})"
        )
    ) %>%
    select(
        sic_3, Corp, `Total Expenditure`, `Services (GNR)`,
        # `General Exp.`,
        `Industrial Exp.`,
        `Deductible Exp.`,
        # `Deductible Inds. Exp.`
    ) %>%
    kbl(
        # format = "html",
        table.attr = 'data-quarto-disable-processing="true"'
    )%>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    collapse_rows(1, valign="top", latex_hline = "major")

```


```{r}
#| label: tbl-corp-vs-all
#| tbl-cap: Comparison of different input over revenue ratios for All types of Juridical Organizations.
#| echo: false
#| warning: false
#| eval: false
#| include: false


colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Comm.")
        ),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        `Corp.` = ifelse(juridical_organization==3,"Corp.","Other"),
        mats_serv_share = mats_serv/sales,
        labor_employee_years_share = labor_employee_years/sales
    ) %>%
    group_by(sic_3,JO) %>%
    summarise( 
       across(
            ends_with("_share"),
            list(
                mean = ~mean(.x, na.rm = TRUE),
                sd = ~sd(.x, na.rm = TRUE)#/sqrt(n())*1.96
            )
        )
    ) %>%
    mutate(
        Energy  = str_glue("{round(consumed_energy_share_mean,1)} ({round(consumed_energy_share_sd,2)})"),
        Capital = str_glue(
            "{round(capital_share_mean,2)} ({round(capital_share_sd,2)})"
        ),
        Labor = str_glue(
            "{round(labor_employee_years_share_mean,2)} ({round(labor_employee_years_share_sd,2)})"
        ),
        `Skilled Labor` = str_glue(
            "{round(skilled_labor_share_mean,2)} ({round(skilled_labor_share_sd,2)})"
        ),
        `Unskilled Labor` = str_glue(
            "{round(unskilled_labor_share_mean,2)} ({round(unskilled_labor_share_sd,2)})"
        ),
        Industry = factor(sic_3)
    ) %>%
    ungroup() %>%
    select(
        Industry, `J.O.`=JO, Energy, Capital, `Skilled Labor`, `Unskilled Labor`
    ) %>%
    kbl(
        # format = "html"
        table.attr = 'data-quarto-disable-processing="true"'
    ) %>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    collapse_rows(1, valign="top", latex_hline = "major")



``` 

```{r}
#| label: tbl-corp-vs-all-exp
#| tbl-cap: Firms' expenses for all types of Juridical Organizations by Industry.
#| echo: false
#| warning: FALSE
#| eval: false
#| include: false

colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Community")
        ),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        Corp = ifelse(juridical_organization==3,"Corp","Other"),
        mats_serv_share = mats_serv/sales,
        labor_employee_years_share = labor_employee_years/sales,
        gen_exp_share = general_expenditure/total_expenditure,
        inds_exp_share = industrial_expenditure/total_expenditure,
        non_deductible_expenses_share = non_deductible_expenses/total_expenditure,
        deductible_expenses_share = deductible_expenses/total_expenditure,
        inds_exp_non_deductible_share = inds_exp_non_deductible/industrial_expenditure,
        inds_exp_deductible_share = inds_exp_deductible/industrial_expenditure,
        total_expenses_share = total_expenditure/sales,
        serv_share = services/total_expenditure
    ) %>%
    group_by(sic_3,JO) %>%
    mutate( n=n()) %>%
    summarise( 
       across(
            ends_with("_share"),
            list(
                mean = ~mean(.x, na.rm = TRUE),
                se = ~sd(.x, na.rm = TRUE)#/sqrt(n)#*1.96
            )
        )
    ) %>%
    mutate(
        `Total Expenditure` = str_glue(
            "{round(total_expenses_share_mean,2)} ({round(total_expenses_share_se,2)})"#,
            # .sep = "\n"
        ),
        `Services (GNR)` = str_glue(
            "{round(serv_share_mean,2)} ({round(serv_share_se,2)})"
        ),
        `General Exp.` = str_glue(
            "{round(gen_exp_share_mean,2)} ({round(gen_exp_share_se,2)})"
        ),
        `Industrial Exp.` = str_glue(
            "{round(inds_exp_share_mean,2)} ({round(inds_exp_share_se,2)})"
        ),
        `Deductible Exp.` = str_glue(
            "{round(deductible_expenses_share_mean,2)} ({round(deductible_expenses_share_se,2)})"
        ),
        `Deductible Inds. Exp.` = str_glue(
            "{round(inds_exp_deductible_share_mean,2)} ({round(inds_exp_deductible_share_se,2)})"
        )
    ) %>%
    select(
        sic_3, `J.O.`=JO, `Total Expenditure`, `Services (GNR)`,
        # `General Exp.`,
        `Industrial Exp.`,
        `Deductible Exp.`,
        # `Deductible Inds. Exp.`
    ) %>%
    kbl(
        # format = "html",
        table.attr = 'data-quarto-disable-processing="true"'
    )%>%
    kable_classic(full_width=F, html_font = "Cambria") %>%
    collapse_rows(1, valign="top", latex_hline = "major")

```


::: {#tbl-reg-shares layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| results: asis

colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Community")
        ),
        Corp = ifelse(juridical_organization==3,"Corp","Other"),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        mats_serv_share = mats_serv/sales,
        materials_share = materials/sales,
        labor_employee_years_share = labor_employee_years/sales,
        gen_exp_share = general_expenditure/sales,
        inds_exp_share_exp = industrial_expenditure/total_expenditure,
        non_deductible_expenses_share_exp = non_deductible_expenses/total_expenditure,
        deductible_expenses_share_exp = deductible_expenses/total_expenditure,
        inds_exp_non_deductible_share = inds_exp_non_deductible/industrial_expenditure,
        inds_exp_deductible_share = inds_exp_deductible/industrial_expenditure,
        total_expenses_share = total_expenditure/sales,
        serv_share_exp = services/total_expenditure,
        energy_serv_share = (consumed_energy+industrial_expenditure)/sales
    ) %>%
    feols(
        sw(
            capital_share,
            consumed_energy_share,
            materials_share
            ) ~ Corp|
        sic_3+metro_area_code+year,
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        div.class = "table"
    )


```

Shares of Revenue for different inputs by Corporations and Non-Corporation.

:::

::: {#tbl-reg-shares-2 layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| results: asis

colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Community")
        ),
        Corp = ifelse(juridical_organization==3,"Corp","Other"),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        mats_serv_share = mats_serv/sales,
        materials_share = materials/sales,
        labor_employee_years_share = labor_employee_years/sales,
        gen_exp_share = general_expenditure/sales,
        inds_exp_share_exp = industrial_expenditure/total_expenditure,
        non_deductible_expenses_share_exp = non_deductible_expenses/total_expenditure,
        deductible_expenses_share_exp = deductible_expenses/total_expenditure,
        inds_exp_non_deductible_share = inds_exp_non_deductible/industrial_expenditure,
        inds_exp_deductible_share = inds_exp_deductible/industrial_expenditure,
        total_expenses_share = total_expenditure/sales,
        serv_share_exp = services/total_expenditure,
        energy_serv_share = (consumed_energy+industrial_expenditure)/sales
    ) %>%
    feols(
        sw(
            skilled_labor_share,
            unskilled_labor_share,
            total_expenses_share
            ) ~ Corp|
        sic_3+metro_area_code+year,
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        div.class = "table"
    )



```

Shares of Revenue for different inputs by Corporations and Non-Corporation.

:::

::: {#tbl-reg-shares-3 layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| results: asis

colombia_data_frame %>%
    ungroup() %>%
    filter(
        sales>0
    ) %>%
    mutate(
        JO = factor(
            juridical_organization, 
            levels = 0:9, 
            labels = c(
                "Proprietorships",
                "Ld. Partnership",
                "Collective",
                "Corporation",
                "De Facto Corp.",
                "Joint Partnership",
                "Joint Stock Co.",
                "Cooperative",
                "Official Entity",
                "Religious Community")
        ),
        Corp = ifelse(juridical_organization==3,"Corp","Other"),
        capital_share = capital/sales,
        consumed_energy_share = consumed_energy/sales,
        mats_serv_share = mats_serv/sales,
        materials_share = materials/sales,
        labor_employee_years_share = labor_employee_years/sales,
        gen_exp_share = general_expenditure/sales,
        inds_exp_share_exp = industrial_expenditure/total_expenditure,
        non_deductible_expenses_share_exp = non_deductible_expenses/total_expenditure,
        deductible_expenses_share_exp = deductible_expenses/total_expenditure,
        inds_exp_non_deductible_share = inds_exp_non_deductible/industrial_expenditure,
        inds_exp_deductible_share = inds_exp_deductible/industrial_expenditure,
        total_expenses_share = total_expenditure/sales,
        serv_share_exp = services/total_expenditure,
        energy_serv_share = (consumed_energy+industrial_expenditure)/sales
    ) %>%
    feols(
        sw(
            serv_share_exp,
            inds_exp_share_exp,
            deductible_expenses_share_exp
            ) ~ Corp|
        sic_3+metro_area_code+year,
        data = ., cluster = ~sic_3+year
    ) %>%
    etable(
        div.class = "table"
    )


```

Shares of Total Expenses for different classifications of expenses by Corporations and Non-Corporation.

:::

#### Are firms switching Juridical Organization types in the data?

No concerns. Most firms did not change their J.O. Very few changed one time and then stayed in their new JO. Rarely has a firm changed more than once. Over time, around 1-3% of firms in an industry changed J.O. Across industries, around 2% of firms changed J.O. each year.

include a table here