## Empirical Application

Given the fiscal reforms of 1983 and 1986 in Colombia, it is natural to think in a difference-in-difference empirical application to test if the fiscal reforms induced any change in the tax evasion behavior of the firms. We can expect that an increase in either the sales tax or corporate income tax rate would lead to higher levels of evasion.

Among other changes, the fiscal law of 1983 tried to homogenize the sales taxes of the manufacturing industry. The reform reduced from 15 to 10% for some industries; for others, it increased the sales tax from 6 to 10%. Still, some others, like the Food Products industry were exempt and certain others were not affected. See @tbl-vat-summary for a description of the changes documented in @Perry1990. 

The 1983 reform also adjusted the income tax rates for limited liability companies and individuals. For individuals, the income tax rate increased by 8% in most scales, while the maximum was reduced from 56 to 49%. For limited liability companies, the CIT was reduced from 10 to 18%.

To evaluate the change in tax evasion by input cost overreporting due to the change in the sales tax, I apply a triple difference approach. I use corporations in the industries exempted from sales taxes the year before the policy change as the control group. 

Formally, non-corporations in industry $k$, which might have received an increment or decrement in their sales tax rate,

$$
s_{1,j,t}^k=\lambda^k_t+\mu^k_1+e^{VAT}_{j,t}+e^{CIT}_{j,t}+\varepsilon_{jt}
$$

Corporations in industry $k$,
$$
s_{0,j,t}^k=\lambda^k_t+\mu^k_0+\varepsilon_{jt}
$$

Likewise, Non-corporations and Corporations in an industry exempt from sales taxes

$$
\begin{aligned}
    s_{1,j,t}^{E}&=\lambda^{E}_t+\mu^E_1+e^{CIT}_{j,t}+\varepsilon_{jt}\\
    s_{0,j,t}^E&=\lambda^E_t+\mu^E_0+\varepsilon_{jt}
\end{aligned}
$$

Taking the difference between time $t'$ and $t$ in industry $k$ for both, corporations and non-corporations,

$$
\begin{aligned}
    \mathbb{E}[s_{1,j,t'}^k]-\mathbb{E}[s_{1,j,t}^k]&=\Delta_\lambda^k+\Delta_e^{VAT}+\Delta_e^{CIT}\\
    \mathbb{E}[s_{0,j,t'}^k]-\mathbb{E}[s_{0,j,t}^k]&=\Delta_\lambda^k
\end{aligned}
$$

The diff-in-diff method will recover the joint effect of both policy changes,
$$
\mathbb{E}[s_{1,j,t'}^k]-\mathbb{E}[s_{1,j,t}^k]-\left(\mathbb{E}[s_{0,j,t'}^k]-\mathbb{E}[s_{0,j,t}^k]\right)=\Delta_e^{VAT}+\Delta_e^{CIT}
$$

The joint effect might be ambiguous because an increase in the sales tax rate will increase the incentive to overreport inputs cost but a decrease in the CIT might decrease the incentive. 

To recover the effect of the change in the sales tax rate, we can use the firms of the industries that are exempted from the sales tax. Intuitively, exempted firms would not react to the change in the sales tax —which is industry-specific—, but only to the CIT —which affects all industries. 

So we have, 

$$
\begin{aligned}    
    \mathbb{E}[s_{1,j,t'}^k]&-\mathbb{E}[s_{1,j,t}^k]-\left(\mathbb{E}[s_{0,j,t'}^k]-\mathbb{E}[s_{0,j,t}^k]\right)\\ 
    &- \left[\mathbb{E}[s_{1,j,t'}^{E}]-\mathbb{E}[s_{1,j,t}^{E}]-\left(\mathbb{E}[s_{0,j,t'}^{E}]-\mathbb{E}[s_{0,j,t}^{E}]\right)\right]=\Delta_e^{VAT}
\end{aligned}
$$

In regression form,

$$
s_{jt}=\alpha \left[ \mathbb{1}\{t=t'\}\times\mathbb{1}\{\text{treat}=\text{Non-Corp}\}\times\mathbb{1}\{k\not=E\} \right]+\beta'_ZZ_{jt}+\gamma_j+\gamma_t+\varepsilon_{jt}
$$

::: {#tbl-reg-didid layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| results: asis
#| cache: true

did_3_inds <- lapply(
    setdiff(top_20_inds$sic_3,c(311,312)),
    \(x)
    colombia_data_frame %>%
    left_join(sales_tax_change) %>%
    filter(
        # year <= 86,
        JO_class != "Other",
        juridical_organization != 6,
        # juridical_organization %in% c(0, 1, 3)
        # year >= 83
        sic_3 %in% c(x,311)#c(x,311,312) #
    ) %>%
    mutate(
        juridical_organization = factor(juridical_organization),
        metro_area_code = factor(metro_area_code),
        # mats_deduct_share = rowSums(cbind(materials,deductible_expenses), na.rm = TRUE)/sales,
        # energy_non_deduct_share = energy_nondeductibles_share,
        JO_class = factor(
            JO_class, 
            levels = c("Corporation", "Proprietorship", "Ltd. Co.", "Partnership")
        ),
        time = case_when(
            year <= 83 ~ "before",
            .default = as.character(year),
        ),
        time = factor(time, levels = c("before","84","85","86")),
        treat = ifelse(juridical_organization==3,"Corp","Non-Corp"),
        treat_2 = ifelse(JO_class=="Corporation","Corp","Non-Corp"),
        treat_3 = ifelse(sic_3==x,"tax_treat","exempt_ctrl"),
        treat = factor(treat, levels = c("Corp","Non-Corp")),
        treat_2 = factor(treat_2, levels = c("Corp","Non-Corp")),
        year = relevel(factor(year), ref="83"),
        sic_3 = relevel(factor(sic_3), ref="311"),
        treat_3 = factor(treat_3, levels = c("exempt_ctrl","tax_treat"))
    ) %>%
    feols( sw(log_mats_share, log_energy_share, log_fuels_share, log_repair_maint_share) ~ year*treat*treat_3+share_sales_tax+polym(k, l, degree = 2, raw = TRUE)
        | plant+year,
        data = ., cluster=~year#~plant+year
    )
)

names(did_3_inds)<-paste0(setdiff(top_20_inds$sic_3,c(311,312)))

invisible(
for (x in paste0(setdiff(industries$sic_3,c(311,312)))[1:10]){
    etable(
        did_3_inds[[x]],
        keep = c(
            # "%^share",
            # "%^year8(4|5|6):treatNon-Corp:sic_\\d{4}"#,
            "%^year8(4|5|6):treatNon-Corp:treat_3\\w+_\\w+"#,
            # "%^treatNon-Corp$"
        ),
        headers = list(
            Industry=paste0(
                str_sub(
                    paste0(
                        top_20_inds[top_20_inds$sic_3==x,'description'][[1]]
                    ),
                    1,30
                ),
                "..."
            ),#x,#paste0(setdiff(unique(colombia_data_frame$sic_3),c(311,312)))[x]#,
            `Tax Change`=str_to_title(
                paste0(
                    top_20_inds[top_20_inds$sic_3==x,'Change'][[1]]
                )
            )
        ),
        div.class = "table"
    ) |> print()
}
)

```

Log of Inputs Cost Share of Revenue by Industry. Triple diff-in-diff. The reference group is Corporations in industries exempted from the Tax Rate the year before the Reform of 1983 (1982).

:::


### Changes in Composition of Total Expenditure

Depending on the industry, firms might be adjusting different margins, raw materials or other expenses. For example, firms in the non-metallic mineral products industry might not fake raw materials but they can adjust deductible expenses. Another example might be the textile industry. Although the available records and data might not allow for separating expenditures precisely, the evidence shows that firms are significantly adjusting these margins.

@Gandhi2020 defines services as general expenditures minus machinery rental and interest payments. The Colombian survey uses industrial expenditure to calculate intermediate consumption. I identified potentially deductible expenses with information from @Perry1990.


```{r}
#| label: tbl-expenses-type
#| tbl-cap: Classifications of Expenditure.
#| cache: true

kbl(
    exps_tbl,
    align = 'lcccc',
    table.attr = 'data-quarto-disable-processing="true"'
) %>% 
kable_classic(full_width=F, html_font = "Cambria") %>%
# row_spec(c(7,17,18), bold = T, hline_after = T) %>%
row_spec(7, bold = T, hline_after = T) %>%
row_spec(17, bold = T, hline_after = T) %>%
row_spec(18, bold = T, hline_after = T)

```

::: {#tbl-reg-exp-inds layout-ncol="1"}

```{r}
#| results: asis
#| cache: true

did_3_inds_exp <- lapply(
    setdiff(top_20_inds$sic_3,c(311,312)),
    \(x)
    colombia_data_frame %>%
    left_join(sales_tax_change) %>%
    filter(
        # year <= 86,
        JO_class != "Other",
        juridical_organization != 6,
        # juridical_organization %in% c(0, 1, 3)
        # year >= 83
        sic_3 %in% c(x,311)#c(x,311,312) #
    ) %>%
    mutate(
        # services_exp_share = services/total_expenditure,
        # industrial_exp_share = industrial_expenditure/total_expenditure,
        # deductible_exp_share = deductible_expenses/total_expenditure,
        juridical_organization = factor(juridical_organization),
        metro_area_code = factor(metro_area_code),
        JO_class = factor(
            JO_class, 
            levels = c("Corporation", "Proprietorship", "Ltd. Co.", "Partnership")
        ),
        time = case_when(
            year <= 83 ~ "before",
            .default = as.character(year),
        ),
        time = factor(time, levels = c("before","84","85","86")),
        treat = ifelse(juridical_organization==3,"Corp","Non-Corp"),
        treat_2 = ifelse(JO_class=="Corporation","Corp","Non-Corp"),
        treat_3 = ifelse(sic_3==x,"tax_treat","exempt_ctrl"),
        treat = factor(treat, levels = c("Corp","Non-Corp")),
        treat_2 = factor(treat_2, levels = c("Corp","Non-Corp")),
        year = relevel(factor(year), ref="83"),
        sic_3 = relevel(factor(sic_3), ref="311"),
        treat_3 = factor(treat_3, levels = c("exempt_ctrl","tax_treat"))
    ) %>%
    feols( sw(log_services_share, log_energy_share, log_fuels_share, log_repair_maint_share)~ year*treat*treat_3+share_sales_tax+polym(k, l, degree = 2, raw = TRUE)
        | plant+year,
        data = ., cluster=~year#~plant+year
    )
)
names(did_3_inds_exp)<-paste0(setdiff(top_20_inds$sic_3,c(311,312)))
for (x in paste0(setdiff(industries$sic_3,c(311,312)))[1:10]){
    etable(
        did_3_inds_exp[[x]],
        keep = c(
            # "%^share",
            # "%^year8(4|5|6):treatNon-Corp:sic_\\d{4}"#,
            "%^year8(4|5|6):treatNon-Corp:treat_3\\w+_\\w+"
            # "%^year\\d{2}:treatNon-Corp:treat.*",
            # "%^treatNon-Corp$"
        ),
        headers = list(
            Industry=paste0(
                str_sub(
                    paste0(
                        x,"–",
                        top_20_inds[top_20_inds$sic_3==x,'description'][[1]]
                    ),
                    1,30
                ),
                "..."
            ),#x,#paste0(setdiff(unique(colombia_data_frame$sic_3),c(311,312)))[x]#,
            `Tax Change`=str_to_title(
                paste0(
                    top_20_inds[top_20_inds$sic_3==x,'Change'][[1]]
                )
            )
        ),
        div.class = "table"
    )|> print()
}


```


Log of Types of Expenses Share of Total Expenses by Industry. Triple diff-in-diff. The reference group is Corporations in industries exempted from the Tax Rate the year before the Reform of 1983 (1982).

:::

### Parallel Trends

::: {#fig-reg-exp-inds layout-ncol="1"}
```{r}
#| fig-label: Parallel trends
#| echo: false
#| warning: false
#| error: false
#| output: true
#| cache: true

for( x in names(did_3_inds)){
    # png(paste0("Paper/images/graphs/p_trends_",x,".png"), width=10*300, height=6*300, res=300)
    pos_83<- did_3_inds[[x]] |> 
                coef() |> names()|> 
                grep("^(?!.*(id|lhs)).*",x=_, value=TRUE, perl=TRUE) |> 
                grep("^year82:treatNon-Corp:treat.*",x=_) 
    coefplot(
        did_3_inds[[x]],
        # x = NULL,#rep(c(-2,-1,1:8), each=4),
        # horiz=TRUE,
        # keep = "%^year\\d{2}:treatNon-Corp:treat_3\\w+_\\w+",
        keep = "^\\d{2}",
        # keep="%^year\\d{2}:treatNon-Corp:sic_\\d{4}",
        main = paste0(
                str_sub(
                    paste0(
                        x,"–",
                        top_20_inds[top_20_inds$sic_3==x,'description'][[1]]
                    ),
                    1,25
                ),
                "-"
            ),
        dict = c(
            "reset",
            `year81:treatNon-Corp:treat_3tax_treat` = "81",
            `year82:treatNon-Corp:treat_3tax_treat` = "82",
            `year84:treatNon-Corp:treat_3tax_treat` = "84",
            `year85:treatNon-Corp:treat_3tax_treat` = "85",
            `year86:treatNon-Corp:treat_3tax_treat` = "86",
            `year87:treatNon-Corp:treat_3tax_treat` = "87",
            `year88:treatNon-Corp:treat_3tax_treat` = "88",
            `year89:treatNon-Corp:treat_3tax_treat` = "89",
            `year90:treatNon-Corp:treat_3tax_treat` = "90",
            `year91:treatNon-Corp:treat_3tax_treat` = "91"
        ),
        grid = FALSE,
        ref = list(`83`=pos_83+1),
        ref.line = TRUE
    )
    legend("topright", col=1:4,lwd=2,legend=c("inter","mats+ded","mats"))
    # dev.off()
}

```

:::

## Empirical Appendix {.appendix}

### Changes in Sales Tax

::: {#tbl-reg-did-inds layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| error: false
#| results: asis
#| cache: true

tax_changes_inds_regs<-lapply(
    top_20_inds$sic_3,
    \(x)
    colombia_data_frame %>%
        left_join(sales_tax_change) %>%
        filter(
            # year <= 86,
            JO_class != "Other",
            juridical_organization != 6,
            # juridical_organization %in% c(0, 1, 3)
            # year >= 83
        ) %>%
        mutate(
            juridical_organization = factor(juridical_organization),
            metro_area_code = factor(metro_area_code),
            JO_class = factor(
                JO_class, 
                levels = c("Corporation", "Proprietorship", "Ltd. Co.", "Partnership")
            ),
            time = case_when(
                year <= 83 ~ "before",
                .default = as.character(year),
            ),
            time = factor(time, levels = c("before","84","85","86")),
            treat = ifelse(juridical_organization==3,"Corp","Non-Corp"),
            treat_2 = ifelse(JO_class=="Corporation","Corp","Non-Corp"),
            treat = factor(treat, levels = c("Corp","Non-Corp")),
            treat_2 = factor(treat_2, levels = c("Corp","Non-Corp")),
            year = relevel(factor(year), ref="83")
        ) %>%
        filter(
            sic_3 == x
        ) %>%
        feols( share_sales_tax~ year*treat+polym(m, k, l, degree = 2, raw = TRUE)
            | plant,
            data = ., cluster=~year#~plant+year
        )

)

for (x in seq(1,16,4)) {
    etable(
        tax_changes_inds_regs[x:(x+3)],
        keep = c("%year8(4|5|6)","%^treatNon-Corp"),
        headers = list(
                Industry=paste0(top_20_inds$sic_3)[x:(x+3)],
                `Tax Change`=paste0(top_20_inds$Change)[x:(x+3)]
        ),
        div.class = "table"
    )|> print()
}


```


DiD on Sales Taxes by Industry. The Control Group is Corporations in 1983 (1982).

:::

