

The objective of this section is to see if the data shows any patterns consistent with these fiscal reforms.

The regression model is now,

$$
\begin{aligned}
    s_{ijt} =& \beta_0 D_{NC,it} + \beta_1 D_{NC,it} \times D_{ijt} \\ 
    & +D_{NC,it}\times \gamma_t '\Gamma_0+ D_{NC,it} \times D_{ijt}\times \gamma_t'\Gamma_1\\
    & +\gamma_j +  \varepsilon_{ijt}
\end{aligned}
$$

where $\gamma_t$ are year dummies, and it is interacted only with the Non-Corporation dummy variable and the interaction term between Non-Corporation and the characteristic of interest, $D_{ijt}$.

In the following figures, I plot the coefficients of the interaction terms between the year dummies with Non-Corporation, and the interaction between Non-Corporation and the characteristic of interest, $D_{ijt}$. The base year is 1983. 

::: {#fig-who-evades layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| error: false


# load("../Code/Products/910-reg-results.Rdata")

palette("ggplot2")

coefplot(regs_non_corp_time[1:3],
  keep = "%Other:year",
  dict = dict,
  group = list(`Non-Corp` = "^^corp::Other:year::"),
  ref = list("corp::Other:year::83" = 4),
  pch = 16
)

legend(
  "topleft",
  col=1:3,
  lwd=2,
  pch=16,
  legend = c("Non-Corp", "Large Non-Corp", "Exporter Non-Corp")
)

coefplot(regs_non_corp_time[2],
  keep = "non_corp_small",
  dict = dict,
  group = list(`Non-Corp x Small x Year` = "^^non_corp_small::Other:Small L:year::"),
  ref = list("non_corp_small::Other:Small L:year::83" = 15)
)

coefplot(regs_non_corp_time[3],
  keep = "Non-Exporter:",
  dict = dict,
  group = list(`Non-Corp x Non-Exporter x Year` = "^^non_corp_non_exporter::Other:Non-Exporter:year::"),
  ref = list("non_corp_non_exporter::Other:Non-Exporter:year::83" = 15)
)

```


:::


::: {#tbl-who-evades-t layout-ncol="1"}

```{r}
#| echo: false
#| output: asis
#| cache: false

# load("../Code/Products/910-reg-results.Rdata")

# res_df <- wip_df

etable(regs_non_corp_time, dict = dict )


```

:::

:::: {#tbl-who-fxef layout-ncol="1"}

::: {.content-visible when-format="html"}

```{r}
#| echo: false
#| cache: true

sanity_tbl %>%
  mutate(
    across(
      `(1)`:`(3)`,
      ~ replace(.x, type == "CI", NA)
    )
  ) %>%
  select(!type) %>%
  kbl(
    col.names = c("SIC","Corps.","Others","Tax Ev.", "(1)","(2)","(3)"),
    table.attr = 'data-quarto-disable-processing="true"'
  ) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  add_header_above(c(" " = 1, "Elasticities" = 2, "Test" = 1, "SIC FE - Model"=3)) %>%
  collapse_rows(columns = 1, valign = "top")


```

:::

::: {.content-visible when-format="latex"}

```{r}
#| echo: false
#| cache: true

sanity_tbl %>%
  mutate(
    across(
      `(1)`:`(3)`,
      ~ replace(.x, type == "CI", NA)
    )
  ) %>%
  select(!type) %>%
  kbl(
    col.names = c("SIC","Corps.","Others","Tax Ev.", "(1)","(2)","(3)"),
    table.attr = 'data-quarto-disable-processing="true"',
    booktabs = TRUE
  ) %>%
  kable_styling(position="center") %>%
  add_header_above(c(" " = 1, "Elasticities" = 2, "Test" = 1, "SIC FE - Model"=3)) %>%
  collapse_rows(columns = 1, valign = "top")


```

:::

::::




::: {#fig-policy-changes .conten-visible when-format="html" layout-ncol="1"}

```{r}
#| echo: false
#| warning: false
#| error: false
#| cache: true

lapply(
  top_20_inds$sic_3[-1] |> sort(),
  \(x){
    prop_pattrn <- paste0("jo_sic_year::Proprietorship:",x,":82")
    llc_pattrn <- paste0("jo_sic_year::Ltd. Co.:",x,":82")
    tbl_pos_prop <- did_reg |> coef() |> names() |> grep(prop_pattrn,x=_, value=FALSE)
    tbl_pos_llcs <- did_reg |> coef() |> names() |> grep(llc_pattrn,x=_, value=FALSE)
    ref_vec_prop <- tbl_pos_prop+1
    names(ref_vec_prop) <- paste0("jo_sic_year::Proprietorship:",x,":83")
    ref_vec_llcs <- tbl_pos_llcs+1
    names(ref_vec_llcs) <- paste0("jo_sic_year::Ltd. Co.:",x,":83")
    
    coefplot(
      did_reg,
      keep = paste0("%Ltd. Co.:",x), #"%Ltd. Co.:312",
      dict = dict,
      group = list(`JO x SIC x Year`=paste0("^^jo_sic_year::Ltd. Co.:",x,":")),# "^^jo_sic_year::Ltd. Co.:312:"),
      ref = ref_vec_llcs,
      col = "blue", alpha = 0.5,
      main = paste0("Industry ",x)
    )
    coefplot(
      did_reg,
      keep = paste0("%Proprietorship:",x),#"%Proprietorship:312",
      dict = dict,
      group = list(`JO x SIC x Year`=paste0("^^jo_sic_year::Proprietorship:",x,":")),#"^^jo_sic_year::Proprietorship:312:"),
      ref = ref_vec_prop,
      add = TRUE, col = "red", alpha = 0.5,
      x.shift = 0.2
    )
    legend(
      "topleft",
      col=c("blue","red"),
      lwd=2,
      legend = c("LLCs", "Proprietorships")
    )
  }
) |> invisible()

```

::: 